### 2019-08-22 reports/thesis/chapters/5_inference.tex
Use 2 sigma confidence interval when comparing different things in inference
Small revisions

An experiment was conducted to investigate how the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, varied with $h$ and $n$. This was done on a simulated dataset of $n$ standard Normal random variables. For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation of the dataset. The median squared error was obtained by taking the median over all squared errors from the 100 estimates. Figure \ref{fig:inference_BandwidthSelection_error} shows the resulting median squared errors.

@@

The optimal bandwidth for a given $n$ was found numerically. Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $n$. A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimised the log squared error for a given $n$. \emph{MATLAB}'s \texttt{fit(x,y,'smoothingspline')} function was used to fit the smoothing spline which has inbuilt cross validation procedures. The optimisation was done using \emph{MATLAB}'s gradient free \texttt{fminsearch} function, using $h=0.9n^{-1/5}$ as the initial value.

>>>>

An experiment was conducted to investigate how the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, varied with $h$ and $n$. This was done on a simulated dataset of $n$ standard Normal random variables. For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation of the dataset. The median squared error was obtained by taking the median over all squared errors from the 100 estimates. 300 values of $n$ from 10 to $10^6$ and 30 values of $h$ from 0.09 to 1.5 were investigated. Figure \ref{fig:inference_BandwidthSelection_error} shows the resulting median squared errors.

@@

The optimal bandwidth for a given $n$ was found numerically. Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $h$ and $n$. A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimised the log squared error for a given $n$. \emph{MATLAB}'s \texttt{fit(x,y,'smoothingspline')} function was used to fit the smoothing spline which has inbuilt cross validation procedures. The optimisation was done using \emph{MATLAB}'s gradient free \texttt{fminsearch} function, using $h=0.9n^{-1/5}$ as the initial value.
